Experience Report:

### 2010-03-16 doc/icfp-2010/main.tex
*** empty log message ***

\subsubsection{Protocol}

@@

Fault tolerance is achieved by exploiting the statues of workers as
follows. First, tasks are only assigned to workers with either
\of{alive} or \of{pinged} status. Second, whenever a worker executing
a task $t$ moves to status \of{not connected} or \of{unreachable}, the
task $t$ is rescheduled, which means

\subsubsection{Same, Poly and Mono} % TODO: change title

>>>>

\subsubsection{Protocol}\label{sec:protocol}

@@

Fault tolerance is achieved by exploiting the statues of workers as
follows. First, tasks are only assigned to workers with either
\of{alive} or \of{pinged} status. Second, whenever a worker executing
a task $t$ moves to status \of{not connected} or \of{unreachable}, the
task $t$ is rescheduled, which means it is put back in the set of
pending tasks. Whenever a task is completed, any rescheduled copy of
this task is either removed from the set of pending tasks or killed if
it was already assigned to an idle worker.

\subsubsection{Three Network Implementations} % TODO: change title

As explained in Section~\ref{sec:API}, the \of{Network} module is
actually providing three different implementations, according to three
different execution scenarios (namely, \of{Same}, \of{Poly} and
\of{Mono}). There is actually a single, generic implementation, which
is then instantiated in three different ways.
The generic implementation assumes that we are only transmitting
strings over the network, as evident from \of{Assign} and
\of{Completed} messages in the protocol section~\ref{sec:protocol}.
Therefore, the signature for the generic implementation is as follows:
\begin{ocaml}
  generic_compute:
    assign_job:('a -> string * string) ->
    handle:('a * 'c -> string -> ('a * 'c) list)  ->
    ('a * 'c) list -> unit
\end{ocaml}
The first argument \of{assign_job} is a function indicating 
the two strings to pass inside the \of{Assign} message of the protocol.
We can now distinguish the three cases:
\begin{description}
\item[\of{Same}:] in this case, \of{assign_job} is simply returning
  the marshaled closure together with the marshaled value.
\item[\of{Poly}:] in this case, \of{assign_job} is simply
  returning the marshaled value (the first string being meaningless in
  this context).
\item[\of{Mono}:] in this case, \of{assign_job} is immediately
  returning its argument (the first string being meaningless in
  this context).
\end{description}
